```{r}
library(tidyverse)
```

# data set is from the nfl combine, between the years of 2000-2018. The nfl combine data set is constructed of 17 rows of physical tests that most athletes took. The data set also has information about the rounds and picks of each player. 

# name of data set is nfldataset 
```{r}
nfldataset
```



#The Fastest, Average, and slowest Forty Yard dash of every year.
```{r}
nfldataset %>% 
  group_by(Year) %>% 
  summarise(fastest = min(Forty, na.rm = TRUE),
            average_speed = mean(Forty, na.rm = TRUE),
            slowest = max(Forty, na.rm = TRUE)
            )

```



# Average Forty time of players who recorded a Forty yard dash between 2000-2017.
```{r}
mean(nfldataset$Forty, na.rm = TRUE)
```



# All RB's picked in the firsst round in the year 2000.

```{r}
  filter(nfldataset, Pos == "RB", Round == 1, Year == 2002)
```



#filtering data set and customizing results view

```{r}
nfldataset %>% 
  filter(Year == 2017, Round == 1) %>%
  select(Year,Round, Pick,Pos, Player, Forty, BenchReps, Shuttle) %>% 
  arrange(Pick)
```



# All QB's drafted in the first round in the year 2003, they are arranged by how fast they are.
```{r}
nfldataset %>% 
  filter(Year == 2015, Pos == "DE", Round == 1) %>% 
  arrange(Pick)
```



# filters the Year and Round and displays a point graph where you can see the Forty times of every pick in the 1st Round.

```{r}
nfldataset %>% 
  filter(Year == 2017, Round == 1) %>% 
  select(Pick, Forty) %>% 
  ggplot() +
  geom_point(mapping = aes(Pick, Forty, color = factor(Pick), size = 3))
```



# Filters to extract data of what year and round is picked, and displays every pick in the round regarding to position so you can see the players that got drafted by their position. 

```{r}
nfldataset %>% 
  filter(Year == 2016, Round == 1) %>%
  select(Year,Round, Pick,Pos, Player, Forty, BenchReps, Shuttle) %>% 
  arrange(Year, Round, Pick) %>% 
  ggplot() +
  geom_point(mapping = aes(Pos, Pick, size = 3, color = factor(Pos)))
 
```



#How many players get drafted if thier speed is above 4.50 in the first round. Total of 17

```{r}
nfldataset %>% 
  filter(Round == 1, Forty >= 4.50, Year == 2001) %>% 
  count()
```



# How many players get drafted in the first round if their speed is below 4.50. Count 15

```{r}
nfldataset %>% 
  filter(Round == 1, Forty <= 4.50, Year == 2001) %>% 
  count()
```



# How many players between 2000-2018 with a speed under 4.50 that got drafted in 1st round. Count 180

```{r}
nfldataset %>% 
  filter(Round == 1, Forty <= 4.50) %>% 
count()
```



# How many players between 2000-2018 with a speed voer 4.50 that got drafted in 1st round. Count 388

```{r}
nfldataset %>% 
  filter(Round == 1, Forty >= 4.50) %>% 
count()
```



#players who run a 4.50 or slower are more likely to get drafted after the 10th pick. 
```{r}
nfldataset %>% 
  filter(Round == 1, Forty >= 4.50, Year == 2005) %>% 
ggplot() +
  geom_point(mapping = aes(Pick, Pos, size = 2 , color = factor(Pos)))
```

#the fastest players are likely to be drafted mostly in the fisrt ten picks of the first round.
```{r}
nfldataset %>% 
  filter(Round == 1, Forty <= 4.50, Year == 2017) %>% 
ggplot() +
  geom_point(mapping = aes(Pick, Pos, size = 2 , color = factor(Pos)))
```

